Supplementary Materials for: ``Well-Designed Environmental Markets Enable Large-Scale Marine Conservation''

### 2019-10-15 docs/Supplementary_materials.tex
Updated docs folder

@@

\section{Supplementary tables and figures}

@@

\begin{figure}
	\centering
	\includegraphics{img/effort_and_revenues.pdf}
	\caption{\label{fig:effort_and_revenues}Effort and revenue in Patch 1 for a combination of reserve sizes ($R$), different within-country movement ($\theta$), and with and without trading. With trading, the relative drop in effort is always larger than the relative drop in revenue as $R$ increases. The exact opposite relationship holds without trading: effort remains fixed as revenue declines with increasing $R$.}
\end{figure}

\begin{figure}
\centering
\includegraphics{img/fishing_raster_diff.png}
\caption{\label{fig:fishing_raster_diff}Change in spatial footprint of analyzed vessels. Black lines show Exclusive Economic Zone (EEZ), red lines show Marine Protected Areas. Panels A and B show the change through time (after - before) for displaced (A) and non-displaced vessels (B). Panel C shows the difference between A and B (displaced - non-displaced), highlighting areas where displaced vessels redistributed to, relative to non-displaced vessels. Note that displaced vessels allocate more hours to the Gilbert Islands and Line islands EEZs, but also Tuvalu and the high seas surrounding PIPA and Kiribati's EEZ.}
\end{figure}

\begin{figure}
\centering
	\includegraphics{img/hist_kir_fishing.pdf}
	\caption{\label{fig:hist_kir_fishing}Ridgeplot for the density of the \% of total fishing hours that took place within Kiribati EEZ waters by year for displaced vessels where the unit of observation is an individual vessel. The vertical lines represent the median of each year.}	
\end{figure}

\begin{figure}
\centering
	\includegraphics{img/all_PS_VDS_cty_year.pdf}
	\caption{\label{fig:all_PS_VDS_cty_year}Annual vessel-days for all PNA countries, by country.}
\end{figure}

>>>>

We observe four characteristics for every vessel: crew size, engine power, vessel length, and tonnage capacity. Figure \ref{fig:balance_density_plot} shows the distribution of these variables for each group of vessels. Table \ref{tab:balance_table} present the mean, and standard deviation of each observable. Group of vessels are similar on observables, and choice to fish inside PIPA before implementation does not appear to be driven by observable characteristics.

\begin{table}[h]

\caption{\label{tab:balance_table}Mean values on observable characteristics by vessel for displaced (n = 64), and non-displaced vessels (n = 254). Numbers in parentheses indicate standard deviation. The last column contains the difference in means (t-scores), with asterisks inicating significant differences as indicated by a two-tailed t-test (* p < 0.1; ** p< 0.05; *** p < 0.01).}
\centering
\begin{tabular}{l|l|l|l}
\hline
Characteristic & Non-displaced & Displaced & Difference\\
\hline
Crew size (n) & 30.46 (6.25) & 26.38 (3.94) & -4.08 (-6.49) ***\\
\hline
Engine Power (KW) & 2559.89 (588.28) & 2983.6 (558.76) & 423.71 (5.36) ***\\
\hline
Length (m) & 68.97 (8.42) & 74.23 (9.71) & 5.25 (3.97) ***\\
\hline
Tonnage (GT) & 1383.41 (533.56) & 1718.14 (653.38) & 334.73 (3.79) ***\\
\hline
\end{tabular}
\end{table}

@@

\section{Supplementary figures}

@@

\begin{figure}
	\centering
	\includegraphics{img/effort_and_revenues.pdf}
	\caption{\label{fig:effort_and_revenues}Effort and revenue in Country 1 for a combination of reserve sizes ($R$), different within-country movement ($\theta$), and with and without trading. With trading, the relative drop in effort is always larger than the relative drop in revenue as $R$ increases. The exact opposite relationship holds without trading: effort remains fixed as revenue declines with increasing $R$.}
\end{figure}

\begin{figure}
\centering
\includegraphics{img/balance_density_plot.pdf}
\caption{\label{fig:balance_density_plot}Distribution of observable characteristics by vessel for displaced (n = 64), non-displaced vessels (n = 254).}
\end{figure}

\begin{figure}
\centering
\includegraphics{img/fishing_raster_diff.png}
\caption{\label{fig:fishing_raster_diff}Change in spatial footprint of analyzed vessels. Black lines show Exclusive Economic Zones (EEZ), red lines show proposed and existing Marine Protected Areas. Panels A and B show the change through time (after - before) for displaced (panel A; n = 64) and non-displaced vessels (panel B; n = 28). Panel C shows the difference between A and B (displaced - non-displaced), highlighting areas where displaced vessels redistributed to, relative to non-displaced vessels. Note that displaced vessels allocate more hours to the Gilbert Islands and Line islands EEZs, but also Tuvalu and the high seas surrounding PIPA and Kiribati's EEZ.}
\end{figure}

\begin{figure}
\centering
	\includegraphics{img/hist_kir_fishing.pdf}
	\caption{\label{fig:hist_kir_fishing}Ridgeplot for the density of the \% of total fishing hours that took place within Kiribati EEZ waters by year for displaced vessels where the unit of observation is an individual vessel (n = 64). The vertical lines represent the median of each year.}	
\end{figure}

\begin{figure}
\centering
	\includegraphics{img/all_PS_VDS_cty_year.pdf}
	\caption{\label{fig:all_PS_VDS_cty_year}Annual country-level vessel-days for all PNA countries by 313 tuna purse seiners.}
\end{figure}
